Instructions for \confname{} Proceedings

### 2019-05-10 papers/EMNLP2019/analysis.tex
done initial annotation pass

\subsection{Crossclassified}

Table

\begin{table*}
  \label{tab:crossclass}
\small
\begin{tabular}{lrl|lrl}
  \toprule
    \multicolumn{3}{c}{same object (217; 31\%)} & \multicolumn{3}{c}{not same object (483; 69\%)}\\
\midrule
co-hyponyms &          104  & horse-donkey, truck-jeep, castle-church & adjacent   &          167 & building-clock, cat-pole, bed-chair\\
overlapping &           69  & skater-boy, cat-toy, horse-statue & supports.1 &          122 & couch-pillow, bowl-fruit, person-dress\\
hypernym.1  &           18  & hat-beanie, jacket-tuxedo, building-hut & part.2     &102& plane-wings, pizza-cheese\\
hypernym.2  &           16  & donut-pastry, train-vehicle, van-automobile & supports.2 &           64 & shirt-child, donut-plate, carpet-floor\\
other       &            8  & sandwich-meal, plane-plain, umbrella-tent & part.1     &           20 & wheel-moped, sink-counter, bread-sub\\
	    & 		    & & other      &           10 & plane-flight, horse-wood\\
\bottomrule
\end{tabular}
\caption{Relations between words or objects when the variants refer to the same object (left) or not (right).}
\end{table*}

@@

\begin{itemize}
\item storefront - store: strictly speaking it's part-whole, but how can one distinguish between the two? 
\item field - grass: same (reverse); how to distinguish?
\item dog - pet (different conceptualizations; classified as ``overlapping''
\item airplane - flight, plane - flight (classified as ``adjacent'' although it's an event relation...)
\end{itemize}

>>>>

\subsection{The ``no relation'' case}

We manually annotated the 100 most frequent name pairs in the ``no relation'' case. Table~\ref{tab:crossclass} shows that, in this category, one third of the pairs do refer to the same object, but the relationship is not captured in WordNet. 
Most of these cases are arguably coverage issues of WordNet, which doesn't capture the co-hyponymy of \textit{horse}-\textit{donkey} or the fact that \textit{vehicle} is hypernym of \textit{train}.\gbt{I find this really weird... also some other cases I annotated. It sounds like I should have listened more carefully to Carina when she suggested going down and up in the wordnet hierarchy (cf.\ the example of food-fruit). :/ Maybe we'd capture quite a bit of them if we did a more sophisticated querying of WordNet. To discuss.}
% between \textit{hat}-\textit{beanie}.
However, a substantial group is constituted by names whose denotations overlap even if they don't belong to the same category. These are typically alternative conceptualizations of objects: as a cat or a toy, as a kind of building or its function (\textit{building}-\textit{home}), or as a portion or a kind of food (\textit{pizza-slice}).

\begin{table*}
  \label{tab:crossclass}
\small
\begin{tabular}{lrl|lrl}
  \toprule
    \multicolumn{3}{c}{same object (215; 31\%)} & \multicolumn{3}{c}{not same object (485; 69\%)}\\
\midrule
co-hyponyms &          148  & horse-donkey, truck-jeep, skier-woman & adjacent   &          167 & building-clock, cat-pole, bed-chair\\
overlapping &           22  & cat-toy, building-home, pizza-slice & supports.1 &          122 & couch-pillow, bowl-fruit, person-dress\\
hypernym.1  &           18  & hat-beanie, jacket-tuxedo, building-hut & part.2     &102& plane-wings, pizza-cheese\\
hypernym.2  &           16  & donut-pastry, train-vehicle, van-automobile & supports.2 &           64 & shirt-child, donut-plate, carpet-floor\\
other       &            8  & sandwich-meal, plane-plain, umbrella-tent & part.1     &           20 & wheel-moped, sink-counter, bread-sub\\
	    & 		    & & other      &           10 & plane-flight, horse-wood\\
\bottomrule
\end{tabular}
\caption{Relations between words or objects when the variants refer to the same object (left) or not (right).}
\end{table*}

Still, 69\% of the annotated pairs arguably do not denote the same object. Here we find problems HUMANS MAKE SAME ``ERRORS'' AS MACHINES -- REFERENTIAL UNCERTAINTY IN THE ABSENCE OF CONTEXT (discuss as planned with Carina).

@@

\begin{itemize}
\item storefront - store: strictly speaking it's part-whole, but how can one distinguish between the two? 
\item field - grass: same (reverse); how to distinguish?
\item dog - pet (different conceptualizations; classified as ``hypernym.2'')
\item airplane - flight, plane - flight (classified as ``other'').
\end{itemize}

Most of the cases are co-hyponyms with categories that are easily confused, such as \textit{horse}-\textit{donkey}, \textit{truck}-\textit{jeep}.
In some cases, the visual cues are not enough to distinguish between the categories, but the frequency of this phenomenon suggests that co-hyponyms can be used interchangeably.
